%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{SOFTWARE ENGINEER} % Job title
{University of Sheffield, Department of Clinical Dentistry} % Organization
{Sheffield, UK} % Location
{Mar. 2020 - PRESENT} % Date (s)
{
    \begin{cvitems} % Description of tasks/responsibilities
    \item{Automating provisioning and management of servers using puppet}
    \item{Working with Ruby on Rails to create a suite of program management applications for department}
    \item{Developing ruby-powered container deployment system}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{INFRASTRUCTURE ENGINEER} % Job title
{Ocado Technology} % Organization
{Hatfield, UK} % Location
{Sep. 2018 - Mar. 2020} % Date (s)
{
    \begin{cvitems} % Description of tasks/responsibilities
    \item{Created tooling to manage monthly rollouts of new data centers.}
    \item{Designed and implemented YANG-based network configuration management application.}
    \item{Created CLI tool for creating virtual test environments to enable regression testing network topology/configuration.}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{BACKEND SOFTWARE ENGINEER (CONTRACT)} % Job title
{Buzzbomb.io} % Organization
{Sheffield, UK} % Location
{Sep. 2017 - Feb. 2018} % Date (s)
{
    \begin{cvitems}
    \item{Built backend for social media search engine powered by Elasticsearch.}
    \item{Designed, implemented, and documented Django REST API.}
    \item{Setup provisioning of production server using Ansible.}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{SOFTWARE ENGINEER (PLACEMENT)} % Job title
{Codethink Ltd.} % Organization
{Manchester, UK} % Location
{Jun. 2017 - Sep. 2017} % Date (s)
{
    \begin{cvitems}
    \item{Acted as lead developer on a small team developing internal Django app.}
    \item{Gathered requirements from across the business and produced a technical specification for the project.}
    \item{Leveraged docker-compose to automate setup of development environment.}
    \item{Worked on backend REST api as well as frontend Vue application.}
    \end{cvitems}
}

%---------------------------------------------------------
\cventry
{STUDENT SOFTWARE ENGINEER (PLACEMENT)} % Job title
{Plusnet Plc.} % Organization
{Sheffield, UK} % Location
{Jun. 2016 - Sep. 2016} % Date (s)
{
    \begin{cvitems}
    \item{Worked as part of a team to build a Spring Boot app for managing software releases.}
    \item{Automated the collection of relevant data from: CGit, Jenkins, and Atlassian JIRA.}
    \item{Created a deployment pipeline using Docker and Jenkins.}
    \item{Built a RESTful API that could be called to interact with collected data.}
    \item{Designed the schema for the MySQL database and set up Flyway database versioning.}
    \end{cvitems}
}

\end{cventries}
