%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Python Instructor} % Affiliation/role
    {Code First Girls} % Organization/group
    {Sheffield, UK} % Location
    {Sep. 2017 - Jan. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designed and ran classes to teach fundamentals of programming using Pyhton.}
        \item {Participated in community outreach to encourage more diversity in the University of Sheffield's tech scene.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Co-Founder \& Lead Organizer} % Affiliation/role
    {HackSheffield} % Organization/group
    {Sheffield, UK} % Location
    {Feb. 2016 - Jul. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item{Worked with and lead a team of 6 to organise, run, and promote HackSheffield MLH hackathons.}
      \item{Reached out to companies and raised sponsorship funding for the first and second event.}
      \item{Helped to increase membership of the society from 0 to 250 members.}
      \item{Organised a trip for 8 people to compete in the HackUPC hackathon in Barcelona.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {First Year Representative} % Affiliation/role
    {University of Sheffield Computer Science Society} % Organization/group
    {Sheffield, UK} % Location
    {Sep. 2015 - Jun. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item{Promoted Computer Science Society events to fellow first year students.}
      \item{Helped to organise and run the University of Sheffield’s first Game Jam (a hackathon based around game development).}
      \item{Designed and ran 5 week ‘Introduction to Linux’ course for class of 20 students.}
      \end{cvitems}
    }

\end{cventries}
